Create Label Density

### 2022-02-15 eda/calculate_label_density.Rmd
updated descriptions
sorting out labeled amicus file

Now we can find the top 5 chunks with the highest label density for each of the frames. If

@@

```{r}
box_write(df, dir_id = "154895322313", "highest_label_density_chunks.csv")
```

>>>>

Now we can find the top 5 chunks with the highest label density for each of the frames. If there are more than 5 chunks with the highest label density, then all are added to the final data frame.

@@

```{r}
#box_write(df, dir_id = "154895322313", "highest_label_density_chunks.csv")
```

# Label Distribution in Manually Labeled Dataset

Read in labeled dataset

```{r}
labeled_amicus <- box_read("913003480881") %>% 
  janitor::clean_names()
```

## Distribution

Get an idea of the distribution of labels that exist in current dataset

```{r}
labeled_amicus %>%
  separate_rows(., hm_label_code_s, sep = "; ", convert = FALSE) %>% 
  select(case, text, hm_label_code_s) %>% 
  group_by(hm_label_code_s) %>% 
  summarize(n=n()) %>% arrange(-n)
```

## Extract text and "true" labels

Note that some of the texts were split in half in order to avoid going over token limit of transformers. These are denoted as "top" or "bottom" and we can get that split by getting the len of each text and taking the first or second half. In cases where the split is not in half, the top or bottom text have been entered.

```{r}
labeled_amicus <- labeled_amicus %>% 
  mutate(manual_divide = ifelse(!is.na(divided_1) | !is.na(divided_2), 1, 0))

# d1
d1_am <- labeled_amicus %>% filter(!is.na(divided_1)) %>% 
  select(case:fem, -text, divided_1,d1_label_code) %>% 
  rename(text = divided_1,label = d1_label_code)
```

```{r}
labeled_amicus %>% 
  filter(!is.na(divided_2) & !is.na(divided_1))
```
